Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Small fix

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
accessible as Datalad (RRID:SCR_003931) datasets.

>>>>

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
accessible as Datalad (RRID:SCR\_003931) datasets.
